\chapter{Inspiration}
\label{ch:kap2}

\section{Research}
\label{sec:Research}
The characters are built around stereotypes, these types of stereotypes have existed for ages. They can all be found in the "The Breakfast Club" \cite{BreakFastClub}.
There you will find among others the "Princess", "Athlete", "Criminal", "Brain" and last but not least "Basket Case". In today's modern society they would more be refereed to as "Mean Girl" or "Queen Bee", "Jock" or sometimes "Bullies", "Delinquent" or "Thug", "Geek" or "Nerd", "Outcast" or "Freak". None of these nicknames are particularly nice, but cliques are a big part of the American High School.\cite{Cliques}. There is several other clique types, but it will take to long time and much space to mention them all. 

\subsection{Originality}
\label{sec:originality}
As mentioned earlier in section \ref{sec:Description}, the concept of originality, in short terms:copying an idea or concept and than use it in another way, change it. Our game "CardLords High School" has probably not been done before, certainly not in this way. A high school theme is not exactly original, it has been done thousands of times before. There is a lot of High School themed games and movies out there, but what makes ours different it's the style. The entire high school is made out of cardboard, and the characters too.    


\section{Games}
\label{sec:Games}
This is a list of some of the different games, we were inspired by, and just like the concept of it. 

\subsection{Game.1}
\label{sec:paperMario}
\textbf{Paper Mario} is of of the main inspiration sources for the game. The idea was having these \textit{"flat"} 2D characters exists in a 3D world. Paper Mario is a perfect example of this, and it also shows us how it great it works. This gave us a lot of ideas such as making the props also out of cardboard. Like the sky in Paper Mario looks like props made of either paper or cardboard.\cite{PaperMario}.

\subsection{Game.2}
\label{sec:SouthParks}

\subsubsection{South Park Series:}

\textbf{South Park The Stick of Truth} and \textbf{South Park Fractured, But Whole}.
These games where kind of important for the characters movement, and a big inspiration for the combat. South Park and Paper Mario has a key element in common and that is using two-dimensional characters in a 3D environment. In addition to this, it also has this RPG element along with the turn-based combat which is heavily implemented in our game. These games are also amusing when it comes to continuously pushing the boundaries when it comes to stereotypes.   
\cite{SouthPark1}
\cite{SouthPark2}

\subsection{Game.3}
\label{sec:darkestDungeon}
\textbf{Darkest Dungeon} is what the animation in our game is influenced by, the design choices \textit{"Red Hook Studios"} did when developing their game. It uses simple keyposes and sliding just to express the characters actions and movement.
\cite{DarkestDungeon}

\subsection{Game.4}
\textbf{The Legend of Bum-bo} is a puzzle game with heavy and dark themes along with a complete use of cardboard look. This is the cardboard style, that has been the primary source of  inspiration for the cardboard look in our game. However our game has a lot more lighthearted concept, so we decided to use some color to give the game more colorful and brighter atmosphere.
\cite{LegendOfBumbo}

\subsection{Game.5}
\textbf{Yoshi's Crafted world} is a platformer game that is playful with it's visual design and color.It is also quite playful with the use of simulated materials from the real world, such as glass bottles, toys and of course cardboard. 
\cite{YoshisCraftedWorld}

\subsection{Game.6}
\textbf{Pokemon} is where the turn-based combat sequences are heavily inspired and influenced by, not just for the technical aspects of it, but also for the visuals as well. This includes the visual element such as the UI, and the choices the player may make like the choice to attack, use item or just flee from the battle.
\cite{Pokemon}

\subsection{Game.7}
\textbf{World Of Warcraft} in this game, often called \textit{"WOW"} there was a lot of inspiration for it. We really wanted to implement, some of the key element in WOW, which is quest and achievements. This is important for the players motivation, Which can bring a lot of enjoyment and something other to do that just battle all the time. Unfortunately we did not get to implement it, only problem was time that stopped us.
\cite{Wow}

\subsection{Game.8}
Final Fantasy VII
\cite{FinalFVII}

\section{Movies}
\label{Movies}
This is a list of some of the movies or series, were inspiration came from.

\subsection{Movie.1}
The BreakFast Club
\cite{BreakFastClub}

\subsection{Movie.2}
The High Musical
\cite{HighSchoolMusical}

\subsection{Movie.3}
Totally Spies
\cite{TotallySpies}

\subsection{Movie.4}
The Marvelous Misadventure of FlapJack
\cite{FlapJack}

\section{Other Sources}
\label{sec:Other}


\subsection{Memes}
\label{sec:Memes}

\section{Music}
\label{sec:Music}