\chapter{Concept}
\label{ch:kap3}
In order to make something unique and original, we had to think completely outside the box. "Moving beyond a surface-level assessment of originality requires attention to the development of original thought and original work."\cite{ConceptOfOriginality}. Considering that this team mainly consists of Concept Artist, we chose to set our focus on implementing as much 2D elements as possible, which one of their many strengths. Since there is a lot of 3D elements "Assets" the only 3D Artist have gotten assist of on of our Concept Artists, which is great and show us that working together gives us advantages and compensates for our weaknesses and lack. Which in this case where resources, because there is a limit for how much a single person can do. In today's modern society there is movies, games and TV-series in all kinds of genre and are easily accessible for everyone, so much has already been done before. 

After researching the concept of originality across several different articles, there we found a definition that describes it all. "And after all, what is originality? It is merely undetected plagiarism.\cite[p.~645]{OriginallyPlagiarism}.

\section{Game Concept}
\label{sec:GameConcept}
The whole concept of our game is to place 2D characters in a 3D environment, this is an quite exiting combination and gives us a wide open window of opportunities. the most challenging part is combining these quite different elements, which is not usually brought together. The best way we could think of doing it where to make elements in the world look like they where kind of \textit{crafted}.What immediately came to mind where where were making the world environment  

\subsection{Story}
\label{sec:story}

